An elementary and constructive proof of Grothendieck's generic freeness lemma

### 2018-05-15 paper-generic-freeness.tex
Moved the special case to the front

@@

The following proposition is just an instance of Grothendieck's generic
freeness lemma. We present it here because it admits an easier proof.

>>>>

The following proposition is just a special instance of Grothendieck's generic
freeness lemma. We include it here because we want to present its proof, which
is easier and shorter than the proof of the general case. The general proof
will be self-contained and not refer to this one.

@@
